---
title: "Analysis of Tensil Test Data"
author: "Gaolin"
date: "10-9-2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(corrplot)
```

### Experiment setup

Various prototypes of CNTs with varying diameter and chirality were built and relaxed using NPT ensemble at 300K. They then undergo MD based tensile test. 

### Read Tensor test data generated with LAMMPS

```{r, echo = F, warning = F, message= F}

files = list.files("data")
files = paste("data/", files, sep="")

tensil = read.csv(files[1])
nn = c(rep(1, 6), rep(4, 8), 82)
mm = c(104, 122, 139, 191, 69, 87, 111, 129, 146, 163, 181, 198, 77, 94, 82)
diameter = c(82, 95, 109, 150, 55, 68, 89, 102, 116, 129, 143, 157, 61, 75, 111)

tensil = tensil %>% mutate(n = nn[1], m = mm[1], diameter = diameter[1])
glimpse(tensil)

for(i in 2:length(files))
{
  ttt = read.csv(files[i])
  ttt = ttt %>% mutate(n = nn[i], m = mm[i], diameter = diameter[i])
  tensil = rbind(tensil, ttt)
}

tensil$n = factor(tensil$n)
tensil$m = factor(tensil$m)
tensil$diameter = factor(tensil$diameter)

```

### Explore Sigmayy vs Strain

### Investigate the relationship between strain and sigmayy when n = 1 

Sigmayy is plotted against strain for different values of m when n = 1. 

```{r, echo = F, message = F, warning = F}
ggplot(tensil %>% filter(n==1), aes(x = v_strain, y = v_sigmayy, color = m)) + 
  geom_line() +
  xlab("Strain") +
  ylab("Sigmayy") +
  ylim(c(-10, 250))
  ggtitle("Sigmayy vs Strain when n = 1") 

 
ggplot(tensil %>% filter(n==1), aes(x = v_strain, y = v_sigmayy, color = m)) + 
  geom_line() +
  xlab("Strain") +
  ylab("Sigmayy") +
  ylim(c(-10, 250)) +
  ggtitle("Sigmayy vs Strain when n = 1") +
  facet_wrap(~m)
  


```

For n = 1, we notice that sigmayy changes smoothly for higher values of m (m = 122, 139 and 191). For smaller m values (69, 87, 104), we observed some oscillations during plastic stage of the stress test. In general, the pre-fracture point is slightly lower for higher values of m.

### Investigate the relationship between strain and sigmayy when n = 4

Sigmayy is plotted against strain for different m values when n = 4.

```{r, echo = F}

ggplot(tensil %>% filter(n==4), aes(x = v_strain, y = v_sigmayy, color = m)) + 
  geom_line() +
  xlab("Strain") +
  ylab("Sigmayy") +
  ylim(c(-10, 250)) +
  ggtitle("Sigmayy vs Strain when n = 4") 
 

ggplot(tensil %>% filter(n==4), aes(x = v_strain, y = v_sigmayy, color = m)) + 
  geom_line() +
  xlab("Strain") +
  ylab("Sigmayy") +
  ylim(c(-10, 250)) +
  ggtitle("Sigmayy vs Strain when n = 4") +
  facet_wrap(~m)

```

For n = 4, we observed that the curve for sigmayy is smoother when m values are high. The slope of elastic stage seemed to be higher than those carbon nanotube with n = 1. The strain is lower to cause pre-fracture for CNT with n = 4 than those CNT with n = 1.
 
 
### Investigate potential energy vs strain

```{r, echo = F}
ggplot(tensil %>% filter(n == 1 | n== 4), aes(x = v_strain, y = PotEng/1000000, color = m)) + 
  geom_line() +
  xlab("Strain") +
  ylab("Potential Energy (MeV)") +
  facet_wrap(~n)
```

Potential energy went up during elastic and plastic stages and drops drastically during pre-fracture stage. There is an inverse relationship between potential energy and m values.

### Investigate kinetic energy vs strain

```{r, echo = F}

ggplot(tensil %>% filter(n != 82), aes(x = v_strain, y = KinEng, color = m)) + 
  geom_line() +
  xlab("Strain") +
  ylab("Kinetic Energy") +
  ylim(c(0, 45000)) +
  facet_wrap(~n)

```


CNT maintain relatively high kinetic energy for higher m values. 

### Explore correlation among variables

### Overall correlation

#### Get correlation plots for n = 1

```{r, eval = F}
mmm = sort(mm[1:6])

for(i in 1:length(mmm))
{
  ttt = tensil %>% filter(n == 1 & m == mmm[i] & v_strain <= 0.2)
  ttt = cor(ttt[, 3:14])
  mytitle = paste("n = 1, m =", mmm[i])
  corrplot(ttt, method="circle", diag = F, main = mytitle, tl.cex = 0.8, tl.srt = 45, mar=c(0,0,2,0))
}
```

#### Get correlation plots for n = 4

```{r, eval = F}
mmm = sort(mm[7:14])

for(i in 1:length(mmm))
{
  ttt = tensil %>% filter(n == 4 & m == mmm[i] & v_strain <= 0.2)
  ttt = cor(ttt[, 3:14])
  mytitle = paste("n = 4, m =", mmm[i])
  corrplot(ttt, method="circle", diag = F, main = mytitle, tl.cex = 0.8, tl.srt = 45, mar=c(0,0,2,0))
}
```

### Correlation during elastic stage

#### Correlation plot for n = 1 carbon nanotubes before pre-fracture stage

```{r}
mmm = sort(mm[1:6])

for(i in 1:length(mmm))
{
  ttt = tensil %>% filter(n == 1 & m == mmm[i] & v_strain <= 0.1)
  ttt = cor(ttt[, 3:14])
  mytitle = paste("n = 1, m =", mmm[i])
  corrplot(ttt, method="circle", diag = F, main = mytitle, tl.cex = 0.8, tl.srt = 45, mar=c(0,0,2,0))
}
```

#### Correlation plot for n = 4 carbon nanotubes before pre-fracture stage

```{r}
mmm = sort(mm[7:14])

for(i in 1:length(mmm))
{
  ttt = tensil %>% filter(n == 4 & m == mmm[i] & v_strain <= 0.2)
  ttt = cor(ttt[, 3:14])
  mytitle = paste("n = 4, m =", mmm[i])
  corrplot(ttt, method="circle", diag = F, main = mytitle, tl.cex = 0.8, tl.srt = 45, mar=c(0,0,2,0))
}

```

### Find maximum sigmayy, potential energy and kinetic energy for each (n,m) combination

```{r}
max_values = tibble(n = numeric(), m = numeric(), sigmayy = numeric(), PE = numeric(), KE = numeric())

for(i in 1:(length(nn)-1))
{
  ttt = tensil %>% filter(n == nn[i] & m == mm[i])
  t_max = c(n = nn[i], m = mm[i], sigmayy = max(ttt[, 5]), PE = max(ttt[, 7]), KE = max(ttt[, 8]))
  max_values = bind_rows(max_values, t_max)
}

max_values$n = factor(max_values$n)


ggplot(max_values, aes(x=m, y = sigmayy, color = n)) +
  geom_point() +
  geom_smooth(se = F)


ggplot(max_values, aes(x=m, y = PE/1000000, color = n)) +
  geom_point() +
  geom_smooth(se = F) +
  ylab("Potential Energy (Mev)") 

ggplot(max_values, aes(x = m, y = KE, color = n)) +
  geom_point() +
  ylim(c(0, 20000)) +
  ylab("Kinetic Energy")

```
 

### Correlation of sigmayy, PE and KE to strain for different chiralities

```{r}
cor_values = tibble(n = numeric(), m = numeric(), sigmayy = numeric(), PE = numeric(), KE = numeric(), stage = character())

for(i in 1:(length(nn)-1))
{
  ttt = tensil %>% filter(n == nn[i] & m == mm[i] & v_strain < 0.1)
  cor_values = cor_values %>%
    add_row(n = nn[i], m = mm[i], sigmayy = cor(ttt[, 3], ttt[, 5]), 
            PE = cor(ttt[,3], ttt[, 7]), 
            KE = cor(ttt[,3], ttt[, 8]), stage = "Elastic")
}

for(i in 1:(length(nn)-1))
{
  ttt = tensil %>% filter(n == nn[i] & m == mm[i] & v_strain >= 0.1 & v_strain < 0.2)
  cor_values = cor_values %>% add_row(n = nn[i], m = mm[i], sigmayy = cor(ttt[, 3], ttt[, 5]), 
            PE = cor(ttt[,3], ttt[, 7]), 
            KE = cor(ttt[,3], ttt[, 8]), stage = "Plastic")
}

cor_values$n = factor(cor_values$n)
cor_values$stage = factor(cor_values$stage)


ggplot(cor_values, aes(x=m, y = sigmayy, color = n, shape = stage)) +
  geom_point(size = 3) +
  ylab("Correlation between strain and sigmayy")


ggplot(cor_values, aes(x=m, y = PE, color = n, shape = stage)) +
  geom_point(size = 3) +
  ylab("Correlation between strain and potential energy")




```


### Find strain needed to reach maximum sigmayy

```{r}
max_sigmayys = tensil %>% filter(n != 82) %>%
  group_by(n, m) %>% slice(which.max(v_sigmayy))

ggplot(max_sigmayys, aes(x = m, y = v_strain, color = n)) +
  geom_point() + 
  ylab("strain")

max_pes = tensil %>% filter(n != 82) %>%
  group_by(n, m) %>% slice(which.max(PotEng))

ggplot(max_pes, aes(x = m, y = v_strain, color = n)) +
  geom_point() + 
  ylab("strain")

max_kes = tensil %>% filter(n != 82) %>%
  group_by(n, m) %>%
  slice(which.max(KinEng))

ggplot(max_kes, aes(x = m, y = v_strain, color = n)) +
  geom_point()
```

 
