---
title: "North Carolina Central University Carbon Nanotube Database"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(tidyverse)
library(plotly)
library(DT)
library(ggcorrplot)
cntParam = readRDS('cntpara.rds')
cntParam = cntParam %>% mutate(par = paste0(n, '-', m, '-', diameter))
tensil = readRDS('tensil.rds')
```



Sidebar {.sidebar}
-----------------------------------------------------------------------

Choose a carbon nanotube configuration.

```{r}

selectInput("par", label = "Choose CNT parameters:",
            choices = cntParam$par, selected = cntParam$par[1])



```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sigmayy vs Strain

```{r}

renderPlotly({
  
  nn = as.numeric(unlist(strsplit(input$par, '-')))
  df = tensil %>% filter(n == nn[1] & m == nn[2] & diameter == nn[3]) 
  
  p1 <- ggplot(df, aes(v_strain, v_sigmayy)) +
    geom_point(color = 'steelblue') +
    labs(title = 'Sigmayy vs Strain')

  ggplotly(p1)
  
  
}) 
  


```

### potential energy vs strain

```{r}
renderPlotly({
  
  nn = as.numeric(unlist(strsplit(input$par, '-')))
  
  df = tensil %>% filter(n == nn[1] & m == nn[2] & diameter == nn[3])

  
  p <- ggplot(df, aes(x = v_strain, y = PotEng)) +
    geom_point(color = 'seagreen') +
    labs(title = 'Potential Energy vs Strain')
  
 ggplotly(p)
  
}) 
  

  
```

### kinetic energy vs strain

```{r}
renderPlotly({
  
  nn = as.numeric(unlist(strsplit(input$par, '-')))
  
  df = tensil %>% filter(n == nn[1] & m == nn[2] & diameter == nn[3])

  
  p <- ggplot(df, aes(x = v_strain, y = KinEng)) +
    geom_point(color = 'red') +
    labs(title = 'Potential Energy vs Strain')
  
 ggplotly(p)
  
}) 
```



### Correlation matrix

#### Choose strain interval
```{r}

sliderInput("strain", label = "Choose the strain levels:",
            min = 0.00006, max = 0.3, step = 0.003, value = c(0.00006, 0.2))  
  

  
```

#### Compute correlation matrix

```{r}
renderPlotly({
  
  nn = as.numeric(unlist(strsplit(input$par, '-')))
  
  df = tensil %>% filter(n == nn[1] & m == nn[2] & diameter == nn[3] & v_strain >= input$strain[1] & v_strain <= input$strain[2])

  
  corr = cor(df[, 3:14])
  
  p = ggcorrplot(corr,method = "square")
  
  
  ggplotly(p)
}) 
```


### Slope Calculation

#### Choose strain interval
```{r}

sliderInput("strain2", label = "Choose the strain levels:",
            min = 0.00006, max = 0.3, step = 0.003, value = c(0.00006, 0.2))  
  
```

#### Compute Slopes
Please choose the interval for strain to compute the slope.
```{r}
renderText({
 
  nn = as.numeric(unlist(strsplit(input$par, '-')))
  x1 = input$strain2[1]
  x2 = input$strain2[2]
  
  df = tensil %>% filter(n == nn[1] & m == nn[2] & diameter == nn[3])
  
  y1 = df %>% filter(v_strain == x1) %>% pull(v_sigmayy)
  y2 = df %>% filter(v_strain == x2) %>% pull(v_sigmayy)
  
  slope = (y2 - y1)/(x2 - x1)
  
  strains = paste0(x1, '-', x2)
  sigmayy = paste0(y1, '-', y2)
  
  slope
  
}) 

```

### Comparative plots

#### Comparative plots of (Sigmayy vs Strain) for different chiralities

```{r}
ggplot(tensil %>% filter(n == 1 | n== 4), aes(x = v_strain, y = v_sigmayy, color = m)) + 
  geom_line() +
  xlab("Strain") +
  ylab("Sigmayy") +
  facet_wrap(~n) + 
  labs(title = "Sigmayy vs strain for different chiralities")
```


#### Comparative plots of (Kinetic energy vs Strain) for different chiralities


```{r}
ggplot(tensil %>% filter(n != 82), aes(x = v_strain, y = KinEng, color = m)) + 
  geom_line() +
  xlab("Strain") +
  ylab("Kinetic Energy") +
  ylim(c(0, 45000)) +
  facet_wrap(~n) +
  labs(title = 'Kinetic energy vs strain for different chiralities')
  
```
