---
title: "North Carolina Central University Carbon Nanotube Database"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(tidyverse)
library(plotly)
library(DT)
library(ggcorrplot)
library(zoo)
```



Sidebar {.sidebar}
-----------------------------------------------------------------------

Select a lammps log file

```{r}
fileInput("file1", "Choose lammps log file in csv format",
                multiple = F,
                accept = c("text/csv",
                         "text/comma-separated-values,text/plain",
                         ".csv"))

dataset <- eventReactive(input$file1,{
      x <- read.csv(input$file1$datapath)
      x <- x %>% mutate(t = Step * 0.0005)
    })

```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### MD Temperature

#### Select an interval
```{r}

sliderInput("MDTime", label = "Choose a MD time interval:",
           min = 0, max = 500, step = 0.0005, value = c(0, 500))  

```

#### Temperature vs MD Time(ps)
```{r}

renderPlotly({

  df = dataset()%>% filter(t >= input$MDTime[1] & t <= input$MDTime[2])
  ggplot(df, aes(t, Temp)) +
    geom_point(color = 'darkred', size = 0.5) +
    labs(x = "MD Time(ps)", y = "Temperature (K)", title = "Temperature changes during MD") 

}) 

```


### strain & stress

#### Strain (linear stimulus during MD)

```{r}

renderPlotly({

  df = dataset() 
  ggplot(df, aes(t, v_strain)) +
    geom_point(color = 'darkred', size = 0.5) +
    labs(x = "MD Time(ps)", y = "strain (unitless)", title = "Strain during MD") 

}) 

```

#### Stresses response during MD

##### Sigmaxx

```{r}
renderPlotly({

  df = dataset() 
  ggplot(df, aes(t, v_sigmaxx)) +
    geom_point(color = 'coral', size = 0.5) +
    labs(x = "MD Time(ps)", y = "Sigmaxx (GPa)", title = "Sigmaxx during MD") 

})
```

##### Sigmayy

```{r}
renderPlotly({

  df = dataset() 
  ggplot(df, aes(t, v_sigmayy)) +
    geom_point(color = 'blue',size = 0.5) +
    labs(x = "MD Time(ps)", y = "Sigmayy (GPa)", title = "Sigmayy during MD") 

})
```

##### Sigmazz

```{r}
renderPlotly({

  df = dataset() 
  ggplot(df, aes(t, v_sigmazz)) +
    geom_point(color = 'seagreen', size = 0.5) +
    labs(x = "MD Time(ps)", y = "Sigmazz (GPa)", title = "Sigmazz during MD") 

})
```

### Potential and Kinetic Energies

#### Potential energy

```{r}
renderPlotly({

  df = dataset()
  ggplot(df, aes(t, PotEng)) +
    geom_point(color = 'darkred', size = 0.5) +
    labs(x = "MD Time(ps)", y = "Potential Energy", title = "Potential Energy during MD") 

})
```


#### Kinetic energy

```{r}
renderPlotly({

  df = dataset()
  ggplot(df, aes(t, KinEng)) +
    geom_point(color = 'blue', size = 0.5) +
    labs(x = "MD Time(ps)", y = "Kinetic Energy", title = "Kinetic Energy during MD") 

})
```


#### Potential + kinetic energy

```{r}
renderPlotly({

  df = dataset() 
  ggplot(df, aes(t, PotEng + KinEng)) +
    geom_point(color = 'seagreen', size = 0.5) +
    labs(x = "MD Time(ps)", y = "Potential + Kinetic Energy", title = "Total Energy during MD") 

})
```



### Size and volume

#### CNT Dimensions (Lx, Ly and Lz)
```{r}
renderPlotly({

  df = dataset()  %>% select(t, Lx, Ly, Lz) %>% 
    gather(dimension, value, Lx:Lz)
  ggplot(df, aes(t, value, color = dimension)) +
    geom_line() + 
    labs(x = "MD Time(ps)", y = "Dimension (A)", title = "CNT Size variation during MD") 

})
```

#### CNT volume and corrected volume

```{r}
renderPlotly({

  df = dataset() %>% select(t, Volume, v_CorVol) %>% 
    gather(volume, value, Volume:v_CorVol)
  ggplot(df, aes(t, value, color = volume)) +
    geom_line() + 
    labs(x = "MD Time(ps)", y = "Volume", title = "CNT Volume and Corrected Volume during MD") 

})
```

#### CNT averaged diameter

```{r}
renderPlotly({

  df = dataset() %>% select(t, v_cntdiameter) 
  
  ggplot(df, aes(t, v_cntdiameter)) +
    geom_line(color = 'blue') + 
    labs(x = "MD Time(ps)", y = "CNT Diameter (A)", title = "CNT averaged diameter during MD") 

})
```

### Stress-strain curves

```{r}
renderPlotly({

  df = dataset() %>% select(v_strain, v_sigmaxx, v_sigmayy, v_sigmazz) %>% 
    gather(dimension, value, v_sigmaxx:v_sigmazz)
  
    ggplot(df, aes(v_strain, value)) +
    geom_line(color = 'blue') + 
    facet_wrap(~dimension) +
    labs(title = "Stress-strain curves along different dimensions")

})
```

### Potential energy features - 1

#### Potential Energy during Initial Pulling and Elastic Regime

```{r}
renderPlotly({

  df = dataset() %>% select(t, PotEng) %>% 
    filter(t>= 0 & t <= 200)
  
  ggplot(df, aes(t, PotEng)) +
    geom_line(color = 'blue') + 
    labs(x = "MD time (fs)", y = "Potential Energy", title = "Potential energy during initial pulling and elastic regime")
})
```

#### Potential Energy during Details of Elastic Regime

```{r}
renderPlotly({

  df = dataset() %>% select(t, PotEng) %>% 
    filter(t>= 150 & t <= 200)
  
  ggplot(df, aes(t, PotEng)) +
    geom_line(color = 'blue') + 
    labs(x = "MD time (fs)", y = "Potential Energy", title = "Potential energy during details of elastic regime")
})
```

#### Potential Energy during Details of the Plastic Regime (just before the fracture)

```{r}
renderPlotly({

  df = dataset()%>% select(t, PotEng) %>% 
    filter(t>= 390 & t <= 404)
  
  ggplot(df, aes(t, PotEng)) +
    geom_line(color = 'blue') + 
    labs(x = "MD time (fs)", y = "Potential Energy", title = "Potential energy during details of elastic regime")
})
```

#### Potential energy during start of instabilities

```{r}
renderPlotly({

  df = dataset() %>% select(t, PotEng) %>% 
    filter(t>= 400 & t <= 404)
  
  ggplot(df, aes(t, PotEng)) +
    geom_line(color = 'blue') + 
    labs(x = "MD time (fs)", y = "Potential Energy", title = "Potential energy during start of instabilities")
})
```


### Potential energy features - 2

#### Select an time interval

```{r}
sliderInput("time2", label = "Choose a MD time interval:",
           min = 0, max = 500, step = 0.0005, value = c(0, 500))  
```

#### Visualize second order variations of potential energy for different stages of time interval


```{r}
# compute rolling of the 30 lagged time points
renderPlotly({

  df = dataset() %>% select(t, PotEng, KinEng) %>% 
    mutate(PotBase = rollmean(PotEng, k = 31, fill=NA), total = PotEng + KinEng) %>% 
    mutate(PotVar = PotEng - PotBase) %>% filter(t >= input$time2[1] & t <= input$time2[2])
  
  ggplot(df, aes(t, PotVar)) +
    geom_line(color = 'seagreen') +
    geom_hline(yintercept = 2.7, color = 'red') +
    geom_hline(yintercept = -2.7, color = 'red') +
    labs(x = "MD time (ps)", y = "Potential Energy Variations (eV)", title = "Second Order Variations of 
Potential Energy (Potential - Baseline)")
})
```

### Plastic events

#### Select an time interval

```{r}
sliderInput("time2", label = "Choose a MD time interval:",
           min = 0, max = 500, step = 0.0005, value = c(0, 500))  
```


```{r}
renderDataTable({
  
    df = dataset() %>% select(t, PotEng, KinEng) %>% 
    mutate(PotBase = rollmean(PotEng, k = 31, fill=NA), total = PotEng + KinEng) %>% 
    mutate(PotVar = PotEng - PotBase) %>% filter(t >= input$time2[1] & t <= input$time2[2]) %>% 
      filter(PotVar > 2.7 | PotVar < -2.7)
  
})
```


### Extracted data

#### Strain-stress curve

```{r}
renderPlotly({

  df = dataset() %>% select(v_strain, v_sigmayy) 
  
  ggplot(df, aes(v_strain, v_sigmayy)) +
    geom_line(color = 'blue') + 
    geom_vline(aes(xintercept=0.077), color="red", linetype="dashed", size=1)+
    geom_vline(aes(xintercept=0.1579), color="red", linetype="dashed", size=1)+
    geom_vline(aes(xintercept=0.255), color="red", linetype="dashed", size=1)+
    geom_vline(aes(xintercept=0.352), color="red", linetype="dashed", size=1)+
    geom_vline(aes(xintercept=0.4031), color="red", linetype="dashed", size=1)+
    labs(x = "strain", y = "Sigmayy (GPa.)", title = "Stress vs Strain Curve")
})
```

#### Elastic modulus

```{r}

sliderInput("strain1", label = "Choose the strain levels:",
            min = 0.0000, max = 0.45, step = 0.003, value = c(0.0005, 0.077))  

renderText({
 
  df = dataset() %>% select(v_strain, v_sigmayy)
  x1 = input$strain1[1]
  x2 = input$strain1[2]
  
  y1 = df %>% filter(v_strain == x1) %>% pull(v_sigmayy)
  y2 = df %>% filter(v_strain == x2) %>% pull(v_sigmayy)
  
  slope = (y2 - y1)/(x2 - x1)
  
  strains = paste0("(", x2, '-', x1, ")")
  sigmayy = paste0("(", y2, '-', y1, ")")
  
  paste0("Elastic modulus = ", sigmayy, "/", strains, " = ", round(slope, 3), " GPa.")
  
}) 

```

#### Plastic modulus

```{r}
sliderInput("strain2", label = "Choose the strain levels:",
            min = 0.0000, max = 0.45, step = 0.003, value = c(0.1579, 0.255))  

renderText({
 
  df = dataset() %>% select(v_strain, v_sigmayy)
  x1 = input$strain2[1]
  x2 = input$strain2[2]
  
  y1 = df %>% filter(v_strain == x1) %>% pull(v_sigmayy)
  y2 = df %>% filter(v_strain == x2) %>% pull(v_sigmayy)
  
  slope = (y2 - y1)/(x2 - x1)
  
  strains = paste0("(", x2, '-', x1, ")")
  sigmayy = paste0("(", y2, '-', y1, ")")
  
  paste0("Plastic modulus = ", sigmayy, "/", strains, " = ", round(slope, 3), " Gpa.")
  
}) 
```

#### Pre-fracture slope

```{r}
sliderInput("strain3", label = "Choose the strain levels:",
            min = 0.0000, max = 0.45, step = 0.003, value = c(0.352, 0.4031))  

renderText({
 
  df = dataset() %>% select(v_strain, v_sigmayy)
  x1 = input$strain3[1]
  x2 = input$strain3[2]
  
  y1 = df %>% filter(v_strain == x1) %>% pull(v_sigmayy)
  y2 = df %>% filter(v_strain == x2) %>% pull(v_sigmayy)
  
  slope = (y2 - y1)/(x2 - x1)
  
  strains = paste0("(", x2, '-', x1, ")")
  sigmayy = paste0("(", y2, '-', y1, ")")
  
  paste0("Pre-fracture slope = ", sigmayy, "/", strains, " = ", round(slope, 3), " GPa.")
  
}) 
```

#### Stress at fracture

```{r}
sliderInput("strain4", label = "Choose the strain levels:",
            min = 0.0000, max = 0.45, step = 0.0003, value = c(0.4032, 0.4036))  

renderText({
 
  df = dataset() %>% select(v_strain, v_sigmayy)
  x1 = input$strain4[1]
  x2 = input$strain4[2]
  
  y1 = df %>% filter(v_strain == x1) %>% pull(v_sigmayy)
  y2 = df %>% filter(v_strain == x2) %>% pull(v_sigmayy)
  y = round((y1+y2)/2, 4)
  
  line1 = paste0("Average stress at fracture = ", y, " GPa.")
  line2 = paste0("Strains at fracture is between ", x1, " and ", x2, "(unitless)")
  paste(line1, line2)
  
}) 
```

